### 2018-07-10 FrascatiPlot/Paper/NucleiB2.tex
first version of summary and conclusions

We conclude that (c.) appears unlikely, thus leaving (b.) as a viable option, at least with our present knowledge of the hypertriton size.

In the following, we summarise our main conclusions:
\begin{enumerate}
	\item Thermal and coalescence models give similar predictions for the production of $A$=2 and $A$=3 (anti-)nuclei in heavy-ion collisions for a source volume that is constrained by experimental data on (anti-)deuteron production.
	\item Thermal and coalescence models give very different predictions for the production of hyper-tritons as a function of source volume in pp, p-Pb, and Pb-Pb collisions. In particular, the yield of hyper-tritons appears to be suppressed by about two orders of magnitude in pp collisions with respect ot the production of \hethree.
\end{enumerate}

In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3827). These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond.

>>>>

%We conclude that (c.) appears unlikely, thus leaving (b.) as a viable option, at least with our present knowledge of the hypertriton size.
While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei, the study presented here shows that large differences are expected for hyper-nuclei with extended wave-functions. In the following, we summarise our main conclusions:
\begin{enumerate}
	\item Thermal and coalescence models give similar predictions for the production of $A$=2 and $A$=3 (anti-)nuclei in heavy-ion collisions for a source volume that is constrained by experimental data on (anti-)deuteron production.
	\item Thermal and coalescence models give very different predictions for the production of hyper-tritons as a function of source volume in pp, p-Pb, and Pb-Pb collisions. In particular, the yield of hyper-tritons appears to be suppressed by about two orders of magnitude in pp collisions with respect ot the production of \hethree. The very limited currently available data on the hyper-triton slightly favors the thermal model prediction.
	\item Systematic measurement in pp, p-Pb, and Pb-Pb collisions at LHC energies show a unique potential to clarify the production mechanism and also the nature of composite QCD objects as they are sensitive to the extension, i.e. the wave-function of the object under study.
\end{enumerate}

In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3827). These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond. In addition, our study is deliberately based on many simplifying assumptions in order to allow for a completely analytical treatment of the problem highlighting. Future studies will be based on more realistic approximations requiring numerical calculations.
